Photovoltaic System Reconfiguration strategy for mismatch condition\\ {\footnotesize \textsuperscript{}}

### 2018-08-13 main.tex
20180813-2

\section{Reconfiguration Algorithm}
The general steps of reconfiguration algorithm are presented in Fig.2. The first step is determine each PV modul's \textit{$V_{mpp}$} and \textit{$I_{mpp}$} by using algorithm provided in \cite{b7} \cite{b9}, and calculate MPP current and voltage candidates of PV array. Afterward, determine real number of working modules per string by applying method in \cite{b10}.

>>>>

\section{Reconfiguration Algorithm}
The general steps of reconfiguration algorithm are presented in Fig.2. The first step is determine each PV modul's \textit{$V_{mpp}$} and \textit{$I_{mpp}$} by using algorithm provided in \cite{b7} \cite{b9}, and calculate MPP current and voltage candidates of PV array. Afterward, determine real number of working modules \textit{$Q_{MN}$}  per string by applying method in \cite{b10}. Next, find maximum output power by multiplying current candidates and voltage candidates which determine by \textit{$Q_{MN}$}.
